---
title: "Day-1 (Data Science)"
author: "Muhammad Farooq"
date: "2022-08-24"
output:
  html_document: default
  pdf_document: default
---
This is our first day of data science course.
My name is Muhammad Farooq and I am a Data scientist student.

Basic Plotting:

1- plot

```{r}
data("iris")
plot(iris$Sepal.Length, iris$Sepal.Width)
```

2- histogram
```{r}
hist(iris$Sepal.Length)
```

3- box plot
```{r}
boxplot(Sepal.Length ~ Species, data = iris)
```

4- image graph
```{r}
x <- matrix(1:120, 12, 10)
x
image(x)
```

5- strip chart
```{r}
stripchart(iris$Sepal.Length)
```

6- qqnorm plot
```{r}
qqnorm(iris$Sepal.Length)
```

Intermediate Plotting:

1- scatter plot
```{r}
data("iris")
plot(iris$Sepal.Length, iris$Sepal.Width, xlab = "Sepal length", ylab = "Sepal Width", main = "Iris Scatter Plot")
```
use the same method to change labels for other plots

2- relational plot
```{r}
plot(iris)
```

corr plot
```{r}
library(corrplot)
```

First of all we need to calculate the correlation
```{r}
c <- cor(iris[,-5])
corrplot(c)
```

Another diverse data set
```{r}
c <- cor(mtcars)
corrplot(c)
```

Number format
```{r}
corrplot(c, method = "number")
```

Upper plot
```{r}
corrplot(c, method = "number", type = "upper")
```

Lower plot
```{r}
corrplot(c, method = "number", type = "lower")
```

Square plot
```{r}
corrplot(c, method = "square", type = "lower")
```

```{r}
corrplot(c, method = "square")
```

```{r}
corrplot(c, method = "shade")
```

Order from high to low
```{r}
corrplot(c, method = "square", type = "lower", order = "AOE")
```

Ellipse plot
```{r}
corrplot(c, method = "ellipse", type = "lower")
```

Mixed corrplot
```{r}
corrplot.mixed(c)
corrplot.mixed(c, lower = "number", upper = "pie", order = "AOE")
```

Clustering
```{r}
corrplot(c, order = "hclust", addrect = 2)
```

Another method of  making a correlation plot
```{r}
library(PerformanceAnalytics)
chart.Correlation(c,  histogram = TRUE, method = "pearson")
```

For more information please visit this link:
https://cran.r-project.org/web/packages/corrplot/vignettes/corrplot-intro.html

Also see this link:
http://r-coder.com/correlation-plot-r/

