---
title: "Day-2"
author: "Muhammad Farooq"
date: "2022-08-26"
output: html_document
---

## This notebook is about statistical methods and their use in our research.
###**List of basic statistical methods**
1- Shapiro wilk's Method
2- t.test (independent, Paired)
3- ANOVA (One way ANOVA and TWO way ANOVA)
4- ANCOVA
5- MANOVA
6- MANCOVA
7- wilcoxon Rank
8- Mann whitney U test
9- Correlation (Pearson and Spearman)
10-Krukshul walis test
11-Regression (Correlation)
12-PostHoc Analysis (Multiple Comparison of Means)

### Check the normal distribution of the data
```{r}
iris
hist(iris$Sepal.Length)
qqnorm(iris$Sepal.Length)
x <- density(iris$Sepal.Length)
plot(x)
```

All these plots can tell us visually if the data is normally distributed.
Another method is to test with Shapiro Wilk's method
```{r}
shapiro.test(iris$Sepal.Length)
```
**Hypothesis: The data is normal.**
*If P-value < 0.05 then we will reject our hypothesis.*
**From the output, the p-value > 0.05 implying that the distribution of the data are not significantly different from normal distribution. In other words, we can say that our data is normal.**

```{r}
hist(iris$Sepal.Width)
qqnorm(iris$Sepal.Width)
y <- density(iris$Sepal.Width)
plot(y)
shapiro.test(iris$Sepal.Width)
```
```{r}
hist(iris$Petal.Length)
qqnorm(iris$Petal.Length)
z <- density(iris$Petal.Length)
plot(z)
shapiro.test(iris$Petal.Length)
```

```{r}
hist(iris$Petal.Width)
qqnorm(iris$Petal.Width)
z1 <- density(iris$Petal.Width)
plot(z1)
shapiro.test(iris$Petal.Width)
```

##t.test
###one sample t.test
```{r}
t.test(iris$Sepal.Length, mu=0)
```

###Tow sample t.test for dependent (two numeric variables should be there)
```{r}
t.test(iris$Sepal.Length, iris$Sepal.Width)
boxplot(iris$Sepal.Length)
boxplot(iris$Sepal.Width)
```

###Tow sample t.test for independent variable (one numeric and one binary factor)
```{r}
x <- subset(iris, iris$Species=="virginica" | iris$Species=="setosa")
x
t.test(x$Sepal.Length ~ x$Species)
```

### Paired t.test (both should be numeric variables)
```{r}
t.test(x$Sepal.Length, x$Sepal.Width, paired = TRUE)
```

###we have to write these p-values in the following order:
p<0.05 *,
p<0.01 **,
p<0.001 ***,

